\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{listings}

\title{Sample Document for Testing LaTeX Import}
\author{Test Author}
\date{December 2024}

\begin{document}

\maketitle

\section{Introduction}

This is a sample LaTeX document to test the Hypermedia LaTeX importer. It includes various LaTeX features that should be converted to Hypermedia blocks.

This paragraph contains \textbf{bold text}, \textit{italic text}, \underline{underlined text}, and \texttt{monospace code}. You can also combine them like \textbf{\textit{bold italic}}.

\section{Mathematical Content}

\subsection{Inline Math}

The famous equation $E = mc^2$ changed our understanding of physics. The quadratic formula is $x = \frac{-b \pm \sqrt{b^2-4ac}}{2a}$.

\subsection{Display Math}

Here is a display equation:

$$\int_{0}^{\infty} e^{-x^2} dx = \frac{\sqrt{\pi}}{2}$$

And using the equation environment:

\begin{equation}
\sum_{n=1}^{\infty} \frac{1}{n^2} = \frac{\pi^2}{6}
\end{equation}

\begin{align}
a &= b + c \\
d &= e + f + g
\end{align}

\section{Lists}

\subsection{Unordered List}

\begin{itemize}
\item First item in the list
\item Second item with some details
\item Third item to complete the list
\end{itemize}

\subsection{Ordered List}

\begin{enumerate}
\item Step one: Initialize the system
\item Step two: Configure the parameters
\item Step three: Run the process
\item Step four: Verify the results
\end{enumerate}

\section{Code Blocks}

Here is a code example using verbatim:

\begin{verbatim}
function hello() {
    console.log("Hello, World!");
    return 42;
}
\end{verbatim}

And using lstlisting:

\begin{lstlisting}[language=Python]
def fibonacci(n):
    if n <= 1:
        return n
    return fibonacci(n-1) + fibonacci(n-2)
\end{lstlisting}

\section{Quotations}

\begin{quote}
This is a quoted block of text. It should be rendered as a blockquote in the Hypermedia document. Quotes are often used to highlight important information or cite sources.
\end{quote}

\section{Links}

You can visit \href{https://example.com}{Example Website} for more information. Or check out \url{https://github.com} directly.

\section{Subsubsection Example}

\subsection{Level 2 Heading}

Some content under a subsection.

\subsubsection{Level 3 Heading}

Content under a subsubsection. This tests the heading hierarchy.

\paragraph{Paragraph Heading}

This is content under a paragraph-level heading.

\section{Conclusion}

This document covers the main LaTeX features supported by the importer:

\begin{itemize}
\item Sections and subsections (headings)
\item Text formatting (bold, italic, underline, code)
\item Inline and display math
\item Ordered and unordered lists
\item Code blocks
\item Blockquotes
\item Links
\end{itemize}

If all these elements render correctly in Hypermedia, the importer is working as expected.

\end{document}
